Technologies of Semantic WEB as an environment of application development and integration

### 2021-11-10 paper-aicts-cherkashin.tex
Revised keywords.

%%
%% Keywords. The author(s) should pick words that accurately describe
%% the work being presented. Separate the keywords with commas.
\begin{keywords}
  knowledge graph \sep
  geographical information system \sep
  semantic web \sep
  storing flexible data \sep
  one-page web application
\end{keywords}

>>>>

%%
%% Keywords. The author(s) should pick words that accurately describe
%% the work being presented. Separate the keywords with commas.
\begin{keywords}
  knowledge graph \sep
  semantic web \sep
  model transformation \sep
  model-driven architecture \sep
  object-oriented logical programming \sep
  web application \sep
  geographical information system
\end{keywords}
